Compositional Certified Resource Bounds

### 2015-04-14 paper/main.tex
bad space tricks on page 10, please check
moved the table to the main body
move table captions on top, trade some space tricks

\begin{table}[t]
\small
\centering
\begin{tabular}{r|c|c|c|c|c}
& KoAT & Rank & LOOPUS & SPEED & \toolname \\
\hline
\#bounds & 9 & 24 & 20 & 14 & 32
\\
\#lin.\ bounds & 9 & 21 & 20 & 14 & 32
\\
\#best bounds & 0 & 0 & 11 & 14 & 29
\\
\#tested & 14 & 33 & 33 & 14 & 33
\end{tabular}
\vspace{.01cm}
\caption{Comparison of $\toolname$ with other
  automatic tools.}
\label{tab:compar}
\end{table}

\begin{table}[t]
\centering
\small
\begin{tabular}{r|c|c|c}
Function & LoC & Bound & Time (s) \\
\hline
\code{adpcm\_coder} & 145 & $1+|[0,\code{N}]|$ & 0.6 \\
\code{adpcm\_decod} & 130 & $1+|[0,\code{N}]|$ & 0.2 \\
\code{BF\_cfb64\_enc} & 151 & $1+2|[-1,\code{N}]|$ & 0.7 \\
\code{BF\_cbc\_enc} & 180 & $2+0.25|[-8,\code{N}]|$ & 1.0 \\
\code{mad\_bit\_crc} & 145 & $61.19{+}0.19|[-1,\code{N}]|$ & 0.4 \\
\code{mad\_bit\_read} & 65 & $1+0.12|[0,\code{N}]|$ & 0.05 \\
\code{MD5Update} & 200 & $133.95{+}1.05|[0,\code{N}]|$ & 1.0 \\
\code{MD5Final} & 195 & 141 & 0.22 \\
\code{sha\_update} & 98 & $2 + 3.55|[0,\code{N}]|$ & 1.2 \\
% \code{build\_ycc\_rgb} & 68 & 257 & 0.05 \\
\code{PackBitsDecode} & 61 & $1+65|[-129,\code{cc}]|$ & 0.6 \\
\code{KMPSearch} & 20 & $1+2|[0,n]|$ & 0.1 \\
\hline
\code{ycc\_rgb\_conv} & 66 & $\code{nr}\cdot\code{nc}$ & 0.1 \\
\code{uv\_decode} & 31 & $\log_2(\code{UV\_NVS})+1$ & 0.1 \\
\end{tabular}
\vspace{.1cm}
\caption{Derived bounds for functions from cBench.}
\label{tab:cbench}
\end{table}

@@

\begin{figure}[t]
\center
\vspace{-.2cm}
\includegraphics[width=.9\linewidth]{fig/bound3d}
\caption{The automatically derived bound $1.33|[x,y]| + 0.33 |[0,x]|$
  (blue lines) and the measured runtime cost (red crosses) for Example
  \emph{t08}. For $x\ge 0$ the bound is tight.}
\label{fig:3d}
\end{figure}

\begin{table*}
\footnotesize

@@

%--------------------------------------------
\end{tabular}
\caption{
  Experimental evaluation comparing the bounds generated KoAT, Rank,
  LOOPUS, SPEED, and our automatic amortized analysis on several
  challenging linear examples. Results for KoAT and SPEED were extracted
  from previous publications because KoAT cannot take C programs as
  input in its current version and SPEED is not available.
  Entries marked with ? indicate that we cannot test the respective example with the tool. Entries
  marked with --- indicate that the tool failed to produce a result. We write
  $\max(a,b)$ for the maximum of $a$ and $b$.
}
\label{tab:eval}
\end{table*}

>>>>

\begin{table}[t]
\nocaptionrule \caption{Comparison of $\toolname$ with other
  automatic tools.}
\vspace{6pt}
\label{tab:compar}
\small
\centering
\begin{tabular}{r|c|c|c|c|c}
& KoAT & Rank & LOOPUS & SPEED & \toolname \\
\hline
\#bounds & 9 & 24 & 20 & 14 & 32
\\
\#lin.\ bounds & 9 & 21 & 20 & 14 & 32
\\
\#best bounds & 0 & 0 & 11 & 14 & 29
\\
\#tested & 14 & 33 & 33 & 14 & 33
\end{tabular}
\vspace{-6pt}
\end{table}

@@

\begin{table*}
\nocaptionrule \caption{
  Experimental evaluation comparing the bounds generated KoAT, Rank,
  LOOPUS, SPEED, and our automatic amortized analysis on several
  challenging linear examples. Results for KoAT and SPEED were extracted
  from previous publications because KoAT cannot take C programs as
  input in its current version and SPEED is not available.
  Entries marked with ? indicate that we cannot test the respective example with the tool. Entries
  marked with --- indicate that the tool failed to produce a result. We write
  $\max(a,b)$ for the maximum of $a$ and $b$.
}
\vspace{6pt}
\label{tab:eval}
\footnotesize

@@

%--------------------------------------------
\end{tabular}
\end{table*}

\begin{table}[t]
\nocaptionrule \caption{Derived bounds for functions from cBench.}
\vspace{6pt}
\label{tab:cbench}
\centering
\small
\begin{tabular}{r|c|c|c}
Function & LoC & Bound & Time (s) \\
\hline
\code{adpcm\_coder} & 145 & $1+|[0,\code{N}]|$ & 0.6 \\
\code{adpcm\_decod} & 130 & $1+|[0,\code{N}]|$ & 0.2 \\
\code{BF\_cfb64\_enc} & 151 & $1+2|[-1,\code{N}]|$ & 0.7 \\
\code{BF\_cbc\_enc} & 180 & $2+0.25|[-8,\code{N}]|$ & 1.0 \\
\code{mad\_bit\_crc} & 145 & $61.19{+}0.19|[-1,\code{N}]|$ & 0.4 \\
\code{mad\_bit\_read} & 65 & $1+0.12|[0,\code{N}]|$ & 0.05 \\
\code{MD5Update} & 200 & $133.95{+}1.05|[0,\code{N}]|$ & 1.0 \\
\code{MD5Final} & 195 & 141 & 0.22 \\
\code{sha\_update} & 98 & $2 + 3.55|[0,\code{N}]|$ & 1.2 \\
% \code{build\_ycc\_rgb} & 68 & 257 & 0.05 \\
\code{PackBitsDecode} & 61 & $1+65|[-129,\code{cc}]|$ & 0.6 \\
\code{KMPSearch} & 20 & $1+2|[0,n]|$ & 0.1 \\
\hline
\code{ycc\_rgb\_conv} & 66 & $\code{nr}\cdot\code{nc}$ & 0.1 \\
\code{uv\_decode} & 31 & $\log_2(\code{UV\_NVS})+1$ & 0.1 \\
\end{tabular}
\vspace{-4pt}
\end{table}

\begin{figure}[t]
\center
\vspace{-.2cm}
\includegraphics[width=.9\linewidth]{fig/bound3d}
\caption{The automatically derived bound $1.33|[x,y]| + 0.33 |[0,x]|$
  (blue lines) and the measured runtime cost (red crosses) for Example
  \emph{t08}. For $x\ge 0$ the bound is tight.}
\label{fig:3d}
\vspace{-10pt}
\end{figure}
